Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-15 icde2016/mdl.tex
moved paper draft into separate subfolders
Small edits

With this interface, we can now define a set of domains for each date part that we wish to be able to parse. These are mostly straightforward enumerations and numeric ranges, each tagged with the ICU format code. Since the ICU parser is flexible about parsing single or double digit formats, we use double-digit formats, but accept one or two digits. One important exception to this rule is for years, which are fixed width fields (2 or 4).

@@

\subsection{Ranking}
MDL structure analysis naturally produces a ranked list of format candidates, but we have found that a number of other properties of the formats should be preferred over simple compactness:
\begin{itemize}
\item Since we have a set of samples, we can apply the candidate format to the strings to see how well it performs. Formats with fewer parse errors are preferred.
\item Date parts can be considered a place-value system, so we prefer ``more significant'' components (\eg month-day-year over hour-minute-second).
\item If two formats from different locales give the same results, prefer the original column locale. The sample set may have missed an example where this could be important.
\item If the format has an ambiguous date order (\eg all days are less than 12), then prefer the default date order of the locale. Again, the sample set may have missed a counterexample, so this is the best option.
\item Once these semantic preferences have been considered, we then prefer the more compact (MDL) representation.
The output of the algorithm is now an ordered list of formats and associated locales. These can then be used to drive a user interface that allows the user to choose between the possibilities or the top-ranking format can simply be used automatically.
\end{itemize}

>>>>

With this interface, we can now define a set of domains for each date part that we wish to be able to parse. These are mostly straightforward enumerations and numeric ranges, each tagged with the ICU format code. Since the ICU parser is flexible about parsing single or double digit formats, we use double-digit formats, but accept one or two digits. One important exception to this rule is for years, which are fixed width fields ($2$ or $4$).

@@

\subsection{Ranking}
MDL structure analysis naturally produces a ranked list of format candidates, but we have found that a number of other properties of the formats should be preferred over simple compactness:
\begin{itemize}
\item Because we have a set of samples, we can apply the candidate format to the strings to see how well it performs. Formats with fewer parse errors are preferred.
\item Date parts can be considered a place-value system, so we prefer ``more significant'' components (\eg month-day-year over hour-minute-second).
\item If two formats from different locales give the same results, prefer the original column locale. The sample set may have missed an example where this could be important.
\item If the format has an ambiguous date order (\eg all days are less than 12), then prefer the default date order of the locale. Again, the sample set may have missed a counterexample, so this is the best option.
\item Once these semantic preferences have been considered, we then prefer the more compact (MDL) representation.
The output of the algorithm is now an ordered list of formats and associated locales. These can then be used to drive a user interface that allows the user to choose between the possibilities or the top-ranking format can simply be used automatically.
\end{itemize}
